A primer to numerical simulations: The perihelion motion of Mercury

### 2018-01-09 tex/MercuryNumerical.tex
Fix name of sample script file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{The code}\label{sec:code}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Below we provide an example script on how to program the visualization of the Mercury orbit in \vpython{}.
\lstinputlisting[language=Python]{Mercury_orbit_base.py}
Further examples and template files can be found online\cite{}.\todo[inline]{@arXiv: online link}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{The code}\label{sec:code}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Below we provide an example script on how to program the visualization of the Mercury orbit in \vpython{}.
\lstinputlisting[language=Python]{mercury_orbit_base.py}
Further examples and template files can be found online\cite{}.\todo[inline]{@arXiv: online link}
